Normalization: A pipeline to analyse time-course gene expression data

### 2019-02-20 scripts/01_quality_control_normalization.Rmd
FIX colors in PCA Plot

meta["Time"] = as.factor(unlist(meta["Time"]))
meta["Replicate"] = as.factor(unlist(meta["Replicate"]))
par(mfrow=c(1, 2))
autoplot(pca_data, data=meta, colour="Group", shape="Replicate")
autoplot(pca_data, data=meta, colour="Time", shape="Replicate")
```

>>>>

meta["Time"] = as.factor(unlist(meta["Time"]))
meta["Replicate"] = as.factor(unlist(meta["Replicate"]))
par(mfrow=c(1, 2))
autoplot(pca_data, data=meta, colour="Group", shape="Replicate") +
    scale_color_manual(values=as.vector(unlist(ann_colors["Group"])))

autoplot(pca_data, data=meta, colour="Time", shape="Replicate") +
    scale_color_manual(values=as.vector(unlist(ann_colors["Group"])))
```
